Evaluate PEER in each cohort and brain region

### 2020-11-19 combined_analysis/eval_resid_in_each.Rmd
Initial commit

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]
  # apply voom
  vobj = voomWithDreamWeights(dge[1:100,], form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))

@@

  PEER_setNk(model,2)

>>>>

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]
  # apply voom
  vobj = voomWithDreamWeights(dge, form_use, info, save.plot=TRUE, BPPARAM = SerialParam())

@@

  PEER_setNk(model,30)
